Raman sideband cooling of single sodium atom to 3D ground state

### 2017-04-18 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] WIP slides

        \draw[<-, line width=1.5] (5.67, 0.1) -- (6, 0.8) node[right] {Carrier};
      }
    }
    \visible<3-> {
      \path (1.75, 4) node {
        \includegraphics[width=8.5cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
      };
      \path (0, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
      };
      \path (6, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
      };
    }
    \visible<4-> {
      \path[blue] (2, 4.6) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{93.1(2.5)\%}$};
      \path[blue] (2, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{91.9(2.3)\%}$};
      \path[blue] (8, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{92.9(2.5)\%}$};
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \path (4, 4) node[fill=blue!80!white,opacity=0.8,text opacity=1,
      text=white!85!yellow,right,align=center,
      rounded corners=0.2cm,inner sep=0.2cm] {
        \textbf{3D ground state:} $79.5(3.6)\%$\\
        \textbf{Loss after cooling:} $15\%$\\\\
        \textbf{Total 3D ground state}\\
        \textbf{preparation fidelity}\\
        $67.6(3.1)\%$
      };
    }
  \end{tikzpicture}
\end{frame}

\begin{frame}{Status}
  \begin{columns}
    \column{5cm}
    \begin{itemize}
    \item Radial-only cooling
    \item<2-> Axial-only cooling
    \item<3-> 3D cooling\\
      (Survival: $\approx 89\%$)
    \end{itemize}
    \vspace{0.5cm}
    \visible<3>{
      \includegraphics[width=5cm]{../../experiments/misc/imgs/data_20170324_010638_a1.png}
    }
    \column{6cm}
    \begin{center}
      \vspace{-1cm}
    \end{center}
  \end{columns}
\end{frame}

@@

\begin{frame}{Axial matrix element}
  \begin{center}
    \includegraphics[width=5cm]{../../calculations/sideband_strength/imgs/coupling.png}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.46_0-6}.png}
  \end{center}
\end{frame}

\begin{frame}{Radial matrix element}
  \begin{center}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.35_0-2}.png}
  \end{center}
\end{frame}

>>>>

        \draw[<-, line width=1.5] (5.67, 0.1) -- (6, 0.8) node[right] {Carrier};
      }
    }
    \visible<3-> {
      \path (1.75, 4) node {
        \includegraphics[width=8.5cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
      };
      \path (0, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
      };
      \path (6, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
      };
    }
    \visible<4-> {
      \path[blue] (2, 4.6) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{93.1(2.5)\%}$};
      \path[blue] (2, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{91.9(2.3)\%}$};
      \path[blue] (8, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{92.9(2.5)\%}$};
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \path (4, 4) node[fill=blue!80!white,opacity=0.8,text opacity=1,
      text=white!90!yellow,right,align=center,
      rounded corners=0.2cm,inner sep=0.2cm] {
        \textbf{3D ground state:} $79.5(3.6)\%$\\
        \textbf{Loss after cooling:} $15\%$\\\\
        \textbf{Total 3D ground state}\\
        \textbf{preparation fidelity}\\
        $67.6(3.1)\%$
      };
    }
  \end{tikzpicture}
\end{frame}

\begin{frame}{Rabi flopping (radial)}
  \begin{center}
    \visible<+->{
      \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}\\
    }
    \visible<+->{
      Good agreement between spectrum and Rabi flopping data.
    }
  \end{center}
\end{frame}

\begin{frame}{Rabi flopping (axial)}
  \begin{center}
    \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_ba.png}\\
    Decoherence caused by magnetic field fluctuation.
  \end{center}
\end{frame}

\begin{frame}{}
  \begin{block}{Conclusion}
    $67.6(3.1)\%$ ground state preparation fidelity {\small ($79.5(3.6)\%$ without loss)}
  \end{block}
  \vspace{1cm}
  \begin{block}{Improvements}
    \begin{itemize}
    \item Reduce off-resonance scattering from Raman beams
    \item Reduce magnetic field fluctuation
    \item Reduce loss during cooling
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}{Axial matrix element}
  \begin{center}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.43_0-6}.png}
  \end{center}
\end{frame}

\begin{frame}{Radial 2 matrix element}
  \begin{center}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.35_0-2}.png}
  \end{center}
\end{frame}

\begin{frame}{Radial 3 matrix element}
  \begin{center}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.29_0-2}.png}
  \end{center}
\end{frame}
